An Airdrop That Preserves Recipient Privacy

### 2019-01-19 paper/defs.tex
defs: better game names (maybe)

\medskip\noindent\textit{Anonymity} means, roughly speaking, that $c$ and $\sig$ reveal
    nothing about $\PK$.
Specifically, consider $\mathsf{Anonym}$, a game between a PPT adversary $\adv$
    and a challenger $\chall$:
%
\begin{itemize}
\item $\chall$ chooses keys $(\PK_0, \SK_0)$, $(\PK_1, \SK_1)$, and sends $(\PK_0, \PK_1)$ to $\adv$.

@@

\end{itemize}
%
$\adv$ wins $\mathsf{Anonym}$ if $b' = b$.

\begin{definition}
Let an adversary $\adv$'s advantage in $\mathsf{Anonym}$ be
$\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} = \sizeof{\probab{\adv~\text{wins}} - \nicefrac{1}{2}}$.
Then an airdrop scheme is \emph{anonymous} if, for any PPT adversary
    $\adv$, $\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} \le \text{negl}$.
\end{definition}

\medskip\noindent\textit{Unforgeability} means, roughly speaking, that
    a party that does not know $\SK$ cannot generate a valid signature
    for any message, even if it knows a valid signature for any other
    message.
Specifically, consider $\mathsf{Unforg}$, a game between a PPT adversary
    $\adv$ and a challenger $\chall$:
%
\begin{itemize}
\item $\chall$ chooses a key $(\PK, \SK)$ and sends $\PK$ to $\adv$.

@@

\end{itemize}
%
$\adv$ wins $\mathsf{Unforg}$ if $\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}$.

\begin{definition}
Let an adversary $\adv$'s advantage in $\mathsf{Unforg}$ be
$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} = \probab{\adv~\text{wins}}$.
Then an airdop is \emph{unforgeable} if, for any PPT adversary $\adv$,
$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} \le \text{negl}$.
\end{definition}

>>>>

\medskip\noindent\textit{Anonymity} means, roughly speaking, that $c$ and $\sig$ reveal
    nothing about $\PK$.
Specifically, consider $\mathsf{Anon}$, a game between a PPT adversary $\adv$
    and a challenger $\chall$:
%
\begin{itemize}
\item $\chall$ chooses keys $(\PK_0, \SK_0)$, $(\PK_1, \SK_1)$, and sends $(\PK_0, \PK_1)$ to $\adv$.

@@

\end{itemize}
%
$\adv$ wins $\mathsf{Anon}$ if $b' = b$.

\begin{definition}
Let an adversary $\adv$'s advantage in $\mathsf{Anon}$ be
$\mathrm{Adv}_{\adv}^{\mathsf{Anon}} = \sizeof{\probab{\adv~\text{wins}} - \nicefrac{1}{2}}$.
Then an airdrop scheme is \emph{anonymous} if, for any PPT adversary
    $\adv$, $\mathrm{Adv}_{\adv}^{\mathsf{Anon}} \le \text{negl}$.
\end{definition}

\medskip\noindent\textit{Unforgeability} means, roughly speaking, that
    a party that does not know $\SK$ cannot generate a valid signature
    for any message, even if it knows a valid signature for any other
    message.
Specifically, consider $\mathsf{Forge}$, a game between a PPT adversary
    $\adv$ and a challenger $\chall$:
%
\begin{itemize}
\item $\chall$ chooses a key $(\PK, \SK)$ and sends $\PK$ to $\adv$.

@@

\end{itemize}
%
$\adv$ wins $\mathsf{Forge}$ if $\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}$.

\begin{definition}
Let an adversary $\adv$'s advantage in $\mathsf{Forge}$ be
$\mathrm{Adv}_{\adv}^{\mathsf{Forge}} = \probab{\adv~\text{wins}}$.
Then an airdop is \emph{unforgeable} if, for any PPT adversary $\adv$,
$\mathrm{Adv}_{\adv}^{\mathsf{Forge}} \le \text{negl}$.
\end{definition}
